WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-14 ms.tex
Explicitly write extrinsic-only likelihood

First, the autocorrelation likelihood has the elegant feature that if we were to replace the autocorrelation function with the \ac{SNR} time series for the best-matching template, $z(\tau; \hat{\mathbf{\theta}}_\mathrm{in})$, we would recover the likelihood for the full \ac{GW} time series, evaluated at the \ac{ML} estimate of the intrinsic parameters. The numerical scheme that we will develop is thus equally applicable for rapid, coincidence-based localization, or as a fast extrinsic marginalization step for the full parameter estimation.

>>>>

First, the autocorrelation likelihood has the elegant feature that if we were to replace the autocorrelation function with the \ac{SNR} time series for the best-matching template, $z(\tau; \hat{\mathbf{\theta}}_\mathrm{in})$, we would recover the likelihood for the full \ac{GW} time series, evaluated at the \ac{ML} estimate of the intrinsic parameters, \emph{viz.}:
%
\begin{equation}\label{eq:extrinsic-only-likelihood}
    % p\left(z_i(\hat{\tau}, \hat{\bm\theta}_\mathrm{in})
        % \middle| \rho_i, \gamma_i, \tau_i \right) \propto \\
    \exp \left[ - \frac{1}{2} \sum_i {\rho_i}^2
        + \sum_i \rho_i \Re \left\{ e^{-i \gamma_i} z_i^*(\tau_i)
        \right\}
    \right].
\end{equation}
%
(We have ommitted the term $\int |Y_i(\omega)|^2/S(\omega)d\omega$, which takes the place of the earlyier ${\hat{\rho}_i}^2$ term and is only important for normalization.) The numerical scheme that we will develop is thus equally applicable for rapid, coincidence-based localization, or as a fast extrinsic marginalization step for the full parameter estimation.
